{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-29 paper/paper.tex
explained NeP3 and NeP4 properties
removed todos
removed todo
fixed spelling

\todo{Explain intuition}

@@

{\small
\begin{enumerate}
\item[NePd] $Dom(next) = \{i \in \mathcal{P} | se(i) = high \land \exists j \in \mathcal{P} . i \mapsto^* j \land se(j) \neq high\}$ \todo{use simple method of new paper?}
\item[NeP1] $i, j \in Dom(next) \land i \mapsto j \Rightarrow next(i) = next(j)$
\item[NeP2] $i \in Dom(next) \land j \not\in Dom(next) \land i \mapsto j \Rightarrow next(i) = j$
\item[NeP3] $j, k \in Dom(next) \land i \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = next(k)$ \todo{is there an error?}
\item[NeP4] $i, j \in Dom(next) \land k \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = k$
\end{enumerate}
}

@@

The domain of next (i.e. NePd) captures the high, but not always high program points (i.e. the ones
that can result in a hidden thread). The property NeP1, states that two directly successive high
program points have the same program point in which the thread becomes visible again. The property NeP2
is the counterpart of the NeP1: If a low program point follows a high program point, this low program
point is the result of the next function for the high program point.

\todo{What is wrong with property 4 (NeP3)}
\todo{What is wrong with property 5 (NeP4)}

@@

The approach also lacks (currently) support for real world languages. For example support of synchronization
would be necessary to implement the approach for Java. The approach of Zdancewic and Myers supports those
features, but is much more restrictive. Due to the use of observational determinism obviously secure programs
like \texttt{l := 1 || l := 0} are rejected. The approach of Barthe et. al. does not reject those programs and
is in that sense much more permissive.

>>>>

@@

{\small
\begin{enumerate}
\item[NePd] $Dom(next) = \{i \in \mathcal{P} | se(i) = high \land \exists j \in \mathcal{P} . i \mapsto^* j \land se(j) \neq high\}$
\item[NeP1] $i, j \in Dom(next) \land i \mapsto j \Rightarrow next(i) = next(j)$
\item[NeP2] $i \in Dom(next) \land j \not\in Dom(next) \land i \mapsto j \Rightarrow next(i) = j$
\item[NeP3] $j, k \in Dom(next) \land i \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = next(k)$
\item[NeP4] $i, j \in Dom(next) \land k \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = k$
\end{enumerate}
}

@@

The domain of next (i.e. NePd) captures the high, but not always high program points (i.e. the ones
that can result in a hidden thread). The property NeP1, states that two directly successive high
program points have the same program point in which the thread becomes visible again. The property NeP2
is the counterpart of the NeP1: If a low program point follows a high program point, this low program
point is the result of the next function for the high program point. NeP3 and NeP4 denote that the
next of an if respective while instruction is at least after the control dependence region.

@@

The approach also (currently) lacks support for real world languages. For example support of synchronization
would be necessary to implement the approach for Java. The approach of Zdancewic and Myers supports those
features, but is much more restrictive. Due to the use of observational determinism obviously secure programs
like \texttt{l := 1 || l := 0} are rejected. The approach of Barthe et. al. does not reject those programs and
is in that sense much more permissive.
